{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-09-28 ident_manu.tex
added ident all figure, L1 to heurist tables

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Sep 27 17:40:51 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms)%
\begin{table}[!tbp]
{\scriptsize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{\bfseries Ammonium}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
\hline
{\bfseries Chlorophyll}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
\hline
{\bfseries Dissolved Oxygen}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$2.31$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.37$\tabularnewline
~~5&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$4.69$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$4.91$\tabularnewline
~~7&\scriptsize{\textit{Zm}}&$3$\textsubscript{Z}&$6.73$\tabularnewline
~~8&\scriptsize{\textit{Zumax}}&$4$\textsubscript{Z}&$6.81$\tabularnewline
\hline
{\bfseries Irradiance}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$7.54$\tabularnewline
~~4&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$8.17$\tabularnewline
~~5&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$9.44$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsubscript{P}&$9.66$\tabularnewline
~~7&\scriptsize{\textit{Zumax}}&$3$\textsubscript{Z}&$10.79$\tabularnewline
\hline
{\bfseries Nitrate}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
\hline
{\bfseries OM1}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
\hline
{\bfseries OM2}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$2.46$\tabularnewline
~~4&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.91$\tabularnewline
\hline
{\bfseries Phosphate}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{vmaxP}}&$2$\textsubscript{P}&$11.48$\tabularnewline
~~4&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$13.74$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:heurist3}} 

@@

\begin{tabular}{llll}

@@

\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline

@@

{\bfseries Ammonium}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.46$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.25$\tabularnewline

@@

{\bfseries Chlorophyll}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.18$\tabularnewline
~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.62$\tabularnewline
~~4&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$3.24$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$5.98$\tabularnewline

@@

{\bfseries Dissolved Oxygen}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$2.29$\tabularnewline
~~4&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.85$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$3.89$\tabularnewline
~~6&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$4.42$\tabularnewline
~~7&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$5.22$\tabularnewline

@@

{\bfseries Irradiance}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{KGcdom}}&$1$\textsubscript{OM}&$4.5$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$4.5$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$6.9$\tabularnewline
~~6&\scriptsize{\textit{ZQn}}&$2$\textsubscript{Z}&$10.63$\tabularnewline
~~7&\scriptsize{\textit{mA}}&$2$\textsubscript{P}&$11.21$\tabularnewline
~~8&\scriptsize{\textit{KG1}}&$2$\textsubscript{OM}&$14.65$\tabularnewline
~~9&\scriptsize{\textit{astarOMA}}&$2$\textsubscript{O}&$14.72$\tabularnewline

@@

{\bfseries Nitrate}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$1$\tabularnewline

@@

{\bfseries OM1}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$3.87$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.93$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$5.81$\tabularnewline

@@

{\bfseries OM2}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.61$\tabularnewline
~~4&\scriptsize{\textit{KG2}}&$1$\textsubscript{OM}&$3.39$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.46$\tabularnewline
~~6&\scriptsize{\textit{umax}}&$2$\textsubscript{P}&$6.02$\tabularnewline
~~7&\scriptsize{\textit{ZKa}}&$2$\textsubscript{Z}&$9.21$\tabularnewline

@@

{\bfseries Phosphate}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsubscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$13.71$\tabularnewline
~~4&\scriptsize{\textit{KG1}}&$1$\textsubscript{OM}&$14.64$\tabularnewline

@@

% identifiability boxplots
\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figs/identbox-1}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.  The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identbox}
\end{figure}

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Sep 28 08:25:08 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms)%
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive (L1, \cref{l1}), until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{tabular}{lllll}
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
{\bfseries Ammonium}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1.54$&$1$\textsubscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1.42$&$1$\textsubscript{Z}&$2.9$\tabularnewline
{\bfseries Chlorophyll}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$13.94$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1.02$&$1$\textsubscript{Z}&$1.18$\tabularnewline
{\bfseries Dissolved Oxygen}&&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$0.05$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$0.05$&$1$\textsubscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{mA}}&$0.02$&$2$\textsubscript{P}&$2.31$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.02$&$1$\textsubscript{T}&$2.37$\tabularnewline
~~5&\scriptsize{\textit{ZQn}}&$0.02$&$2$\textsubscript{Z}&$4.69$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$0.02$&$3$\textsubscript{P}&$4.91$\tabularnewline
~~7&\scriptsize{\textit{Zm}}&$0.02$&$3$\textsubscript{Z}&$6.73$\tabularnewline
~~8&\scriptsize{\textit{Zumax}}&$0.02$&$4$\textsubscript{Z}&$6.81$\tabularnewline
{\bfseries Irradiance}&&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$0.13$&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$0.09$&$1$\textsubscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{ZQn}}&$0.06$&$2$\textsubscript{Z}&$7.54$\tabularnewline
~~4&\scriptsize{\textit{mA}}&$0.05$&$2$\textsubscript{P}&$8.17$\tabularnewline
~~5&\scriptsize{\textit{KGcdom}}&$0.05$&$1$\textsubscript{OM}&$9.44$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$0.04$&$3$\textsubscript{P}&$9.66$\tabularnewline
~~7&\scriptsize{\textit{Zumax}}&$0.04$&$3$\textsubscript{Z}&$10.79$\tabularnewline
{\bfseries Nitrate}&&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
{\bfseries OM1}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$0.96$&$1$\textsubscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$0.92$&$1$\textsubscript{OM}&$3.87$\tabularnewline
{\bfseries OM2}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$2.46$\tabularnewline
~~4&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.91$\tabularnewline
{\bfseries Phosphate}&&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1.47$&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$0.78$&$1$\textsubscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{vmaxP}}&$0.59$&$2$\textsubscript{P}&$11.48$\tabularnewline
~~4&\scriptsize{\textit{ZQn}}&$0.5$&$2$\textsubscript{Z}&$13.74$\tabularnewline

@@

\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the third heuristic where parameters were selected equally within each category from most to least sensitive (L1, \cref{l1}), until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton).\label{tab:heurist3}} 

@@

\begin{tabular}{lllll}

@@

\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline

@@

{\bfseries Ammonium}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1.54$&$1$\textsubscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1.42$&$1$\textsubscript{Z}&$2.9$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.79$&$1$\textsubscript{T}&$3.46$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$0.03$&$1$\textsubscript{O}&$4.25$\tabularnewline

@@

{\bfseries Chlorophyll}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$13.94$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1.02$&$1$\textsubscript{Z}&$1.18$\tabularnewline
~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.6$&$1$\textsubscript{T}&$2.62$\tabularnewline
~~4&\scriptsize{\textit{KGcdom}}&$0.07$&$1$\textsubscript{OM}&$3.24$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$0.02$&$1$\textsubscript{O}&$5.98$\tabularnewline

@@

{\bfseries Dissolved Oxygen}&&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$0.05$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$0.05$&$1$\textsubscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.02$&$1$\textsubscript{T}&$2.29$\tabularnewline
~~4&\scriptsize{\textit{KG1}}&$0.01$&$1$\textsubscript{OM}&$3.85$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$7.51\times 10^{-4}$&$1$\textsubscript{O}&$3.89$\tabularnewline
~~6&\scriptsize{\textit{mA}}&$0.02$&$2$\textsubscript{P}&$4.42$\tabularnewline
~~7&\scriptsize{\textit{ZQn}}&$0.02$&$2$\textsubscript{Z}&$5.22$\tabularnewline

@@

{\bfseries Irradiance}&&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$0.13$&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$0.09$&$1$\textsubscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{KGcdom}}&$0.05$&$1$\textsubscript{OM}&$4.5$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.03$&$1$\textsubscript{T}&$4.5$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$0.02$&$1$\textsubscript{O}&$6.9$\tabularnewline
~~6&\scriptsize{\textit{ZQn}}&$0.06$&$2$\textsubscript{Z}&$10.63$\tabularnewline
~~7&\scriptsize{\textit{mA}}&$0.05$&$2$\textsubscript{P}&$11.21$\tabularnewline
~~8&\scriptsize{\textit{KG1}}&$0$&$2$\textsubscript{OM}&$14.65$\tabularnewline
~~9&\scriptsize{\textit{astarOMA}}&$0$&$2$\textsubscript{O}&$14.72$\tabularnewline

@@

{\bfseries Nitrate}&&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$8.49$&$1$\textsubscript{P}&$1$\tabularnewline

@@

{\bfseries OM1}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$7.22$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$0.96$&$1$\textsubscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$0.92$&$1$\textsubscript{OM}&$3.87$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.86$&$1$\textsubscript{T}&$3.93$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$0.03$&$1$\textsubscript{O}&$5.81$\tabularnewline

@@

{\bfseries OM2}&&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$14.25$&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1.48$&$1$\textsubscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1.01$&$1$\textsubscript{Z}&$2.61$\tabularnewline
~~4&\scriptsize{\textit{KG2}}&$0.94$&$1$\textsubscript{OM}&$3.39$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$0.04$&$1$\textsubscript{O}&$4.46$\tabularnewline
~~6&\scriptsize{\textit{umax}}&$1.11$&$2$\textsubscript{P}&$6.02$\tabularnewline
~~7&\scriptsize{\textit{ZKa}}&$0.88$&$2$\textsubscript{Z}&$9.21$\tabularnewline

@@

{\bfseries Phosphate}&&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1.47$&$1$\textsubscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$0.78$&$1$\textsubscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$0.16$&$1$\textsubscript{T}&$13.71$\tabularnewline
~~4&\scriptsize{\textit{KG1}}&$0.14$&$1$\textsubscript{OM}&$14.64$\tabularnewline

@@

% identifiability plot
\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figs/identplo-1}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.  The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identplo}
\end{figure}

% identifiability plot, all state variables
\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figs/identploall-1}

\caption{Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.  The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$, see \cref{fig:inistreval}).}\label{fig:identploall}
\end{figure}
